canaper: Categorical analysis of neo- and paleo-endemism in R

### 2023-05-14 ms/ms.Qmd
Update ref format don't shorten et al list in refs

---
title: "canaper: Categorical analysis of neo- and paleo-endemism in R"
bibliography: references.yaml
csl: ecography.csl
highlight-style: github
crossref: 
  fig-title: Fig.
  tbl-title: Table
  fig-prefix: Fig.
  tbl-prefix: Table
format:
  docx:
    reference-doc: custom-reference.docx
  pdf:
    include-in-header:
      # keep figures from floating away
      text: |
        \usepackage{float}
        \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
---

>>>>

---
title: "canaper: Categorical analysis of neo- and paleo-endemism in R"
bibliography: references.yaml
csl: oikos.csl
highlight-style: github
crossref: 
  fig-title: Fig.
  tbl-title: Table
  fig-prefix: Fig.
  tbl-prefix: Table
format:
  docx:
    reference-doc: custom-reference.docx
  pdf:
    include-in-header:
      # keep figures from floating away
      text: |
        \usepackage{float}
        \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
---

### 2023-05-14 ms/si.Qmd
Update ref format don't shorten et al list in refs

---
title: "canaper: Categorical analysis of neo- and paleo-endemism in R"
subtitle: "Supporting information"
# FIXME: for double-blind review leave out of submission text, but add after accepted 
# author:
#   - Joel H. Nitta
#   - Shawn W. Laffan
#   - Brent D. Mishler
#   - Wataru Iwasaki
bibliography: references.yaml
csl: methods-in-ecology-and-evolution.csl
highlight-style: github
format:
  pdf:
    include-in-header:
      # keep figures from floating away
      text: |
        \usepackage{float}
        \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
---

>>>>

---
title: "canaper: Categorical analysis of neo- and paleo-endemism in R"
subtitle: "Supporting information"
# FIXME: for double-blind review leave out of submission text, but add after accepted 
# author:
#   - Joel H. Nitta
#   - Shawn W. Laffan
#   - Brent D. Mishler
#   - Wataru Iwasaki
bibliography: references.yaml
csl: oikos.csl
highlight-style: github
format:
  pdf:
    include-in-header:
      # keep figures from floating away
      text: |
        \usepackage{float}
        \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
---
